Cluster Difference Imaging Photometric Survey. II. TOI~837: A Young Validated Planet in IC~2602

### 2020-08-06 paper/ms.tex
cleaning bib

\tn\ joins a number of other young planetary systems reported from
TESS, including DS~Tuc~Ab, HIP~67522b, TOI~1726, and AU~Mic~b
\citep{newton_tess_2019,zhou_well_2019,montet_young_2019,rizzuto_tess_2020,mann_tess_2020,plavchan_planet_2020,palle_transmission_2020,addison_youngest_2020,martioli_magnetism_2020,hirano_limits_2020}.
Figure~\ref{fig:rpvsage} shows \tn\ in the space of planet sizes and
ages.  \tn\ is among the youngest transiting planets known.

>>>>

\tn\ joins a number of other young planetary systems reported from
TESS, including DS~Tuc~Ab, HIP~67522b, TOI~1726, and AU~Mic~b
\citep{newton_tess_2019,zhou_well_2020,montet_young_2020,rizzuto_tess_2020,mann_tess_2020,plavchan_planet_2020,palle_transmission_2020,addison_youngest_2020,martioli_magnetism_2020,hirano_limits_2020}.
Figure~\ref{fig:rpvsage} shows \tn\ in the space of planet sizes and
ages.  \tn\ is among the youngest transiting planets known.
